Extending K-Means Clustering with Ptolemy’s Inequality

### 2024-10-02 main.tex
changes from overleaf, mostly NiAv
proofread first part of results
further proofing, problem with bibliography

\documentclass[english]{lni}

@@

In this short paper, we focus on partitioning methods due to their simplicity in terms of interpretability and implementability \cite{DBLP:conf/iiwas/BeecksBHLSD22}. In this field, the \emph{k-means algorithm} \cite{bock2007clustering,hans2008origins,DBLP:journals/prl/Jain10,steinley2006k} has become one of the most influential clustering techniques \cite{DBLP:journals/kais/WuKQGYMMNLYZSHS08,olukanmi2019rethinking}. Although the term "k-means algorithm" is explicitly credited to MacQueen \cite{macqueen1967}, its origins trace back to Steinhaus \cite{steinhaus1956division} in 1956, with its first application to data clustering by Forgy \cite{forgy1965cluster} in 1965. The widely recognized version in use today is the \emph{Lloyd algorithm} \cite{DBLP:journals/tit/Lloyd82}, introduced in 1982.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{fig/gaussia+random.png}
  \caption{}
  \label{fig:gauss_univariate}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{fig/wine+iris.png}
  \caption{}
  \label{fig:data}
\end{figure}

@@

%%% Angabe der .bib-Datei (ohne Endung) / State .bib file (im Falle der Nutzung von BibTeX)
\bibliography{references,bibliography_thesis,bibliography_iiwas}
%% \printbibliography % im Falle der Nutzung von biblatex
\end{document}

>>>>

@@

In this short paper, we focus on partitioning methods due to their simplicity in terms of interpretability and implementability \cite{DBLP:conf/iiwas/BeecksBHLSD22}. In this field, the \emph{k-means algorithm} \cite{bock2007clustering,hans2008origins,DBLP:journals/prl/Jain10,steinley2006k} has become one of the most influential clustering techniques \cite{DBLP:journals/kais/WuKQGYMMNLYZSHS08,olukanmi2019rethinking}. Although the term \emph{k-means algorithm} is explicitly credited to MacQueen \cite{macqueen1967}, its origins trace back to Steinhaus \cite{steinhaus1956division} in 1956, with its first application to data clustering by Forgy \cite{forgy1965cluster} in 1965. The widely recognized version in use today is the \emph{Lloyd algorithm} \cite{DBLP:journals/tit/Lloyd82}, introduced in 1982.

@@

\input{content/5_results}

@@

\clearpage
%%% Angabe der .bib-Datei (ohne Endung) / State .bib file (im Falle der Nutzung von BibTeX)
\todo{re-enable citations}
%\bibliography{references,bibliography_thesis,bibliography_iiwas}
%% \printbibliography % im Falle der Nutzung von biblatex
\end{document}
